Multiple imputation of incomplete multilevel data using Heckman selection models

### 2022-11-10 1.Paper/Paper.Rmd
Update figures

#### Continuous incomplete variable
 ```{r rhocont,fig.align='center',fig.pos="!htb",fig.cap="\\label{fig:rhocont} Continuous incomplete variable by varing $\\rho$, the dashed line depicts the target performance criteria value",echo=FALSE,fig.keep="last",fig.height = 4, fig.width = 6}
plot_rho
 ```

@@

In case of a bivariate missing variable, we also find (Figure \ref{fig:bin}) that the 2l.Heckman method provides unbiased results on coefficient parameters and random effects when the missing variable is binary. However, we observe more variability in the estimates of random effects, reflected on longer confidence intervals on the Bias and RMSE criteria.

 ```{r rhobin,fig.align='center',fig.pos="!htb",fig.cap="\\label{fig:bin} Binary incomplete variable by varing $\\rho$, the dashed line depicts the target performance criteria value",echo=FALSE,fig.keep="last",fig.height = 4, fig.width = 6}
plot_bin
```

@@

```{r size,fig.align='center',fig.pos="!htb",fig.cap="\\label{fig:size} Continuous incomplete variable under systematical missingness by varing: number of clusters (N); sample size per cluster ($n_i$), the dashed line depicts the true simulated parameter value",echo=FALSE,fig.keep="last",fig.height = 4, fig.width = 6}
plot_N
```

@@

```{r dist,fig.align='center',fig.pos="!htb",fig.cap="\\label{fig:dist} Comparison of methods for continuous incomplete variable with deviations in distribution assumptions, where the dashed line depicts the true simulated parameter value",echo=FALSE,fig.keep="last",fig.height = 4, fig.width = 6}
plot_S
```
<!-- Ideally, the phrase " where the dashed line depicts the true simulated parameter" belongs in a note under the caption. -->

@@

In each sub-district, a sample of households with at least one child aged 2-10 years was surveyed, where information was collected on household conditions and use of preventive measures. In addition, finger prick blood samples were taken from each child to determine the prevalence of parasitaemia and an etymological study was conducted to estimate mosquito prevalence. Details of the project and survey are provided elsewhere. [@staedke2019]

@@

print(xt, comment = FALSE, include.rownames=FALSE,add.to.row = comment,
      hline.after = c(-1,0))
```
<!-- What are non-participants? Children with missing values? -->
According to our imputation approach, non-participants were estimated to have a higher prevalence of malaria than participants in more than half of the districts analyzed. 
As can be seen in Figure \ref{fig:region}, for each subregion the prevalence estimates of the approaches do not differ significantly between methods. However, prevalence estimates under the MNAR assumption (i.e. 2 level Heckman)  are higher than those estimated under the MAR or MCAR aproaches, except for the East-Central region. 
```{r region,fig.align='center',fig.width = 5, fig.asp =.67, fig.pos="!htb", fig.cap="\\label{fig:region} Estimates of malaria prevalence by Uganda subregion",echo=FALSE,fig.keep="last",cache = TRUE}
 plot_dist
```

@@

```{r region_age,fig.align='center', fig.pos="!htb", fig.cap="\\label{fig:region_age} Estimation of malaria prevalence by region and age",echo=FALSE,fig.keep="last",cache = TRUE}
plot_sdist_age
```

>>>>

#### Continuous incomplete variable
 ```{r rhocont,fig.align='center',fig.pos="!htb",fig.cap="Continuous incomplete variable by varing $\\rho$, the dashed line depicts the target performance criteria value",echo=FALSE,fig.keep="last",fig.height = 4, fig.width = 6}
plot_rho
 ```

@@

In case of a bivariate missing variable, we also find (Figure \ref{fig:rhobin}) that the 2l.Heckman method provides unbiased results on coefficient parameters and random effects when the missing variable is binary. However, we observe more variability in the estimates of random effects, reflected on longer confidence intervals on the Bias and RMSE criteria.

 ```{r rhobin,fig.align='center',fig.pos="!htb",fig.cap="Binary incomplete variable by varing $\\rho$, the dashed line depicts the target performance criteria value",echo=FALSE,fig.keep="last",fig.height = 4, fig.width = 6}
plot_bin
```

@@

```{r size,fig.align='center',fig.pos="!htb",fig.cap="Continuous incomplete variable under systematical missingness by varing: number of clusters (N); sample size per cluster ($n_i$), the dashed line depicts the true simulated parameter value",echo=FALSE,fig.keep="last",fig.height = 4, fig.width = 6}
plot_N
```

@@

```{r dist,fig.align='center',fig.pos="!htb",fig.cap="Comparison of methods for continuous incomplete variable with deviations in distribution assumptions, where the dashed line depicts the true simulated parameter value",echo=FALSE,fig.keep="last",fig.height = 4, fig.width = 6}
plot_S
```
<!-- Ideally, the phrase " where the dashed line depicts the true simulated parameter" belongs in a note under the caption. -->

@@

In each sub-district, a sample of households with at least one child aged 2-10 years was surveyed, where information was collected on household conditions and use of preventive measures. In addition, finger prick blood samples were taken from each child to determine the prevalence of parasitemia and an etymological study was conducted to estimate mosquito prevalence. Details of the project and survey are provided elsewhere. [@staedke2019]

@@

print(xt, comment = FALSE, include.rownames=FALSE,add.to.row = comment,
      hline.after = c(-1,0))
```
<!-- What are non-participants? Children with missing values? -->
According to our imputation approach, non-participants were estimated to have a higher prevalence of malaria than participants in more than half of the districts analyzed. 
As can be seen in Figure \ref{fig:region}, for each subregion the prevalence estimates of the approaches do not differ significantly between methods. However, prevalence estimates under the MNAR assumption (i.e. 2 level Heckman)  are higher than those estimated under the MAR or MCAR aproaches, except for the East-Central region. 
```{r region,fig.align='center',fig.width = 5, fig.asp =.67, fig.pos="!htb", fig.cap="Estimates of malaria prevalence by Uganda subregion",echo=FALSE,fig.keep="last",cache=TRUE}
 plot_dist
```

@@

```{r region_age,fig.align='center', fig.pos="!htb", fig.cap="Estimation of malaria prevalence by region and age",echo=FALSE,fig.keep="last",cache = TRUE}
plot_sdist_age
```
